---
title: "R Notebook"
output: html_notebook
---

Run this code to start!
```{r}
artists <- read.csv("moma_artists.csv", as.is=TRUE)
art <- read.csv("artworks.csv", as.is=TRUE)
```

# Continuous vs Categorical Data
Open the `artists` dataframe and get to know the data.

1. What are the variables (columns) in this data set?


2. Which of these are categorical variables?


3. Which are continuous?


Open the `art` dataframe and get to know the data.

4. Put each variable from `art` under either "continuous" or "categorical"
## Continuous:


## Categorical:


# Aggregation & Applying Functions
5. Run the following code, then explain what it does. Hint: `unlist` is a function that flattens vectors-of-vectors into a single-layer vector. `trimws` removes spaces around text.
```{r}
ids <- strsplit(art$Artist.ID, ",")
ids <- unlist(ids) 
ids <- trimws(ids)

t <- table(ids)

artists$numPieces <- t[as.character(artists$Artist.ID)]

artists$numPieces <- ifelse(is.na(artists$numPieces), 0, artists$numPieces)
```


6.. Pick one categorical variable and one continuous variable from either dataframe. Aggregate the *continuous* data over the *categorical* variable. In other words, do some opreation (sum/average/concatenate/?) to all the items of a each category to get one result (number/string) to represent each category.

```{r}

```

7. Use `tapply` to sum the number of pieces by artist nationality. Hint: `artists` now has all the information you need.
```{r}

```

# Scatter Plots
8.. Make a scatter plot charting number of pieces by artist birth year.
```{r}
```

9.. Re-make the same plot but remove the extremely high and extremely low `numPieces` artists. Hint: Use quantiles to do this-- select whatever cutoffs you deem appropriate.
```{r}

```

10. Make a scatter plot of width and height for artworks classified as Paintings.
```{r}
#First, select all the paintings:

#Then remove all those missing either width or height. Hint: use "!is.na()" to check if something isn't NA

#Then, draw the plot:

```

11. Re-make the same plot without the very large items. 
```{r}

```

12. Use `lm()` to find a best-fit line.

```{r}

```
13. What relationship is this best-fit line describing?



14. Get the correlation between the width and height for paintings.
```{r}

```

15. What does the above score indicate?
 
 
16. If you've finished everything else, play around with producing other kinds of plots.